---
title: "Lab 1"
author: "Cameron Kay & Ashley Miller"
date: "4/10/2019"
output:
  html_document:
    theme: spacelab
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include = FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 7.5,
                      fig.height = 4.5)

# load packages
library(tidyverse)
```

### Data structures

```{r daniels_code}
set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
                   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))

```

### Run the above code

#### 1. From the model results: 

  + Extract the qr tolerance (tol).
    
```{r extract_qrtol}
# check the attributes for model
#attributes(m)

# look inside qr_tol
#m$qr

# extract tolerance
(tol <- m$qr$tol)

```

The tolerance is `r round(tol)`. 

  + Extract the term labels from the model.

```{r extract_attributes}
# check the structure of the model
#str(m)

# look term.labels
(term_labels <- attributes(m$terms)$term.labels)
```

The term labels for the model was `r gsub(" d", " and d", paste(term_labels, collapse = ", "))`.
  
  + hint: Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.
    
#### 2. From the list

  + Use at least two different methods to extract m.

```{r 2ash_extractm}

#str(l)

# I need to extract m, with is a list within list a
#method # 1:
l$a$m

#method #2
l[["a"]][["m"]]

```

  + Extract the third column of m. Maintain the dimensions (matrix structure).
 
```{r 2ash_extract3c}

l$a$m[, 3, drop = FALSE]

```
   
  + Use at least two different methods to extract the score for student 7.

```{r 2ash_s7}

#l$b$score

#method 1
l$b$score[7]

#method 2
l[["b"]][["score"]][[7]]

```

### Loops

#### 3. Use the “airquality” dataset, which is part of base R. Split it by Month

```{r airquality_split}
# split by month
aq_split <- split(x = airquality, f = airquality$Month)

aq_split
```

#### 4. Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)

```{r 4ash}

#str(aq_split)

means <- rep(NA, 5)

for(i in seq_along(means)) {
    means[i] <- mean(aq_split[[i]][, 1], na.rm = TRUE) #calculates mean of column 1 (Ozone) for each list
}

means

```

#### 5. Replicate this calculation with lapply, sapply, and vapply

```{r star_apply}
# compute ozone mean for each month and output list
lapply(aq_split, function(x) mean(x$Ozone, na.rm = TRUE))

# computer ozone mean for each month and output an atomic vector
sapply(aq_split, function(x) mean(x$Ozone, na.rm = TRUE))

# computer ozone mean for each month and specify output as a double
vapply(aq_split, function(x) mean(x$Ozone, na.rm = TRUE), FUN.VALUE = double(1))

```

#### 6. Produce a plot showing the relation between Ozone and Solar.R for each month.

```{r ozone_solar_plots}
# create a plot for each month
plots_by_month <- lapply(aq_split, function(x) {
  ggplot(x, aes(Ozone, Solar.R)) +
    geom_point() +
    geom_smooth()
})

plots_by_month

```

#### 7. Use a for loop to save the plots to a folder on your computer

```{r 7ash_forloop_plots}

filenames <- here::here("plots", 
                        paste0("month", names(plots_by_month), ".png"))
filenames

for(i in seq_along(plots_by_month)) {
    ggsave(filenames[i], # single bracket
           plots_by_month[[i]], # double bracket
           device = "png",
           width = 6.5, 
           height = 8)
}

```

